\entry{Course \mbox{competencies}}
{This course will allow the student to fully achieve the competency:

OOUS: Analyze various situations and phenomena in physics using the basic laws of electricity and magnetism.
\begin{enumerate}
\item Analyze situations in physics associated with static electric charge and electric current.
\item Analyze situations in physics associated with magnetism and magnetic induction.
\item Apply the laws of electricity and magnetism.
\item Verify experimentally a number of laws of electricity and magnetism.
\end{enumerate}
\smallskip
This course also contributes to partially achieve the competency:

OOUU:	Apply acquired knowledge to one or more subjects in the sciences.
\begin{enumerate}
\item Recognize the contribution of more than one scientific discipline to certain situations.
\item Apply the experimental method.
\item Solve problems.
\item Use data-processing technologies.
\item Reason logically.
\item Communicate effectively.
\item Show evidence of independent learning in their choice of documentation or laboratory instruments.
\item Work as members of a team.
\item Make connections between science, technology and social progress.
%\item To identify the underlying values underlying their treatment of a topic% NOT IN MINISTRY DOC?
%\item To place scientific concepts used in a historical context% NOT IN MINISTRY DOC?
%\item To show attitudes appropriate for scientific work% NOT IN MINISTRY DOC?
%\item To apply acquired knowledge and skills to new situations% NOT IN MINISTRY DOC?
\end{enumerate}
}
